\textbf{How open are hybrid journals included in transformative agreements?}

### 2024-02-27 analysis/manuscript.Rmd
one more glitch
Drafting abstract and declarations

```{r country_top_20_plot, fig.asp=0.8, fig.cap="Development of open access in hybrid journals in transformative agreements between 2018 and 2022, by the Top 20 most productive countries in terms of total articles published in the five-years period. Blue areas represent open access through transformative agreements, the grey areas depict open access articles where no link to an agreement could be established. Country names are represented as ISO two-letter country codes"}
country_plot
```

@@

>>>>

```{r country_top_20_plot, fig.asp=0.8, fig.cap="Development of open access in hybrid journals in transformative agreements between 2018 and 2022, by the Top 20 most productive countries in terms of total articles published in the five-years period. Blue areas represent open access through transformative agreements, the grey areas depict open access articles where no link to an agreement could be established. Country names are represented as ISO two-letter country codes. Facet subheadings show the total number of articles and corresponding market share."}
country_plot
```

@@

# Competing interests

The author declares no competing interests.

# Funding information

This work was supported by the Deutsche Forschungsgemeinschaft (Grant number 416115939).

# Data and code availability

Source code analysis including data used is available on GitHub: <https://github.com/njahn82/hoa_ta_effects>.

### 2024-02-27 analysis/manuscript.tex
one more glitch
Drafting abstract and declarations

%\authornote{Correspondence concerning this article should be addressed to Najko Jahn}

\abstract{}

@@

\caption{Development of open access in hybrid journals in transformative agreements between 2018 and 2022, by the Top 20 most productive countries in terms of total articles published in the five-years period. Blue areas represent open access through transformative agreements, the grey areas depict open access articles where no link to an agreement could be established. Country names are represented as ISO two-letter country codes}\label{fig:country_top_20_plot}
\end{figure}

@@

>>>>

\authornote{ORCID: https://orcid.org/0000-0001-5105-1463}

\abstract{Ongoing controversies surrounding transformative agreements as a means of transitioning journal publishing to full open access highlight the need for large-scale studies assessing the adoption of open access in hybrid journals, including the extent to which transformative agreements contributed to it. Combining publicly available data from various sources, including cOAlition S Journal Checker, Crossref, and OpenAlex, this study presents a novel approach that leverages metadata from over 700 agreements and nine million journal articles.  Estimates suggest a strong growth in open access between 2018 and 2022 from 4.3\% to 15\%. In 2022, 58\% of open access articles could be attributed to transformative agreements. Growth can be largely attributed to three large commercial publishers: Elsevier, Springer Nature, and Wiley, but it varies substantially across journals, publishers, disciplines, and country affiliations. These estimates indicate that the current level of implementation of transformative agreements is insufficient to bring about a large-scale transition to full open access. In particular, different developments in the OECD and BRICS areas have the potential to hinder the transition of academic journal publishing. These findings are important for researchers and stakeholders engaged in negotiating and evaluating these agreements.}

\keywords{hybrid open access, transformative agreements, scholarly publishing, big deals, bibliometrics}

@@

\caption{Development of open access in hybrid journals in transformative agreements between 2018 and 2022, by the Top 20 most productive countries in terms of total articles published in the five-years period. Blue areas represent open access through transformative agreements, the grey areas depict open access articles where no link to an agreement could be established. Country names are represented as ISO two-letter country codes. Facet subheadings show the total number of articles and corresponding market share.}\label{fig:country_top_20_plot}
\end{figure}

@@

\hypertarget{competing-interests}{%
\section{Competing interests}\label{competing-interests}}

The author declares no competing interests.

\hypertarget{funding-information}{%
\section{Funding information}\label{funding-information}}

This work was supported by the Deutsche Forschungsgemeinschaft (Grant
number 416115939).

\hypertarget{data-and-code-availability}{%
\section{Data and code availability}\label{data-and-code-availability}}

Source code analysis including data used is available on GitHub:
\url{https://github.com/njahn82/hoa_ta_effects}.
